Twitter Data Analysis

### 2019-05-04 csci260/wordCountingApp/twitter.tex
started my portion

\section{Methodology}
\tab ***David Write your stuff here***

@@

\newpage
\begin{thebibliography}{}
	\bibitem{stuff}I don't think we need any references, do we?

>>>>

\section{Methodology}
\tab In order to collect the tweet data for the analysis, this study chose to use the Twitter API (*** Reference? ***). To do so, the program used to access the tweet metadata needed to be registered through a twitter developer account.

@@

\newpage
\begin{thebibliography}{}
	\bibitem{stuff}https://twitter.com
	\bibitem{stuff}https://developer.twitter.com/en/docs.html *** CHECK THIS ***
